Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
value -> spectral flux density

Using the expressions above, we find that the radio spectral flux density observed at the Earth is:
%%%
\begin{eqnarray}
F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 \nu_{\rm cyc}} \\
&\approx & 5.2\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupiter-twin)} \notag \\
%%%
&\approx & 0.70 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot}/{\rm yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
&\approx & 0.70 \times 10^{-3} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{10^{-5} M_{\odot}/{\rm yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
%%%
&\approx & 2.4 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
\end{eqnarray}
%%%
Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters. 
Compared with the equivalent Jupiter-like planets around main sequence stars, the massive stellar wind of late red giants can increase the radio emission from planetary companions by more than 2 orders of magnitude, which allow us to explore 10 times more distant system, i.e., 1000 times more volume. This compensates the small population of evolved stars at least partly.

Equation (\ref{eq:F_nu_RGHJ}) gives the value which is orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial values and full ionization. This mainly originates from that their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind, while the scaling law for the planetary magnetic field strength is also different.

>>>>

Using the expressions above, we find that the radio spectral flux density observed at the Earth is:
%%%
\begin{eqnarray}
F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 \nu_{\rm cyc}} \\
&\approx & 5.2\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupiter-twin)} \notag \\
%%%
&\approx & 0.70 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot}/{\rm yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
&\approx & 0.70 \times 10^{-3} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{10^{-5} M_{\odot}/{\rm yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
%%%
&\approx & 2.4 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
\end{eqnarray}
%%%
Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters. 
Compared with the equivalent Jupiter-like planets around main sequence stars, the massive stellar wind of late red giants can increase the radio emission from planetary companions by more than two orders of magnitude, which allow us to explore 10 times more distant system, i.e., 1000 times more volume. This compensates the small population of evolved stars at least partly.

Equation (\ref{eq:F_nu_RGHJ}) gives a spectral flux density that 1--2 orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial values and full ionization.
This is primarly because their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind, while the scaling law for the planetary magnetic field strength is also different.
